Multiple Round Ballot Polling Risk-Limiting Audit Simulations

### 2021-10-19 MultipleRoundSims/MultipleRoundSims.tex
minerva explanation

\subsection{Minerva}
For Minerva, it has not been shown that round sizes can be chosen
during the audit. That is, an adversary with knowledge of the history
of the audit may be able to choose round sizes which cause the 
risk of the audit to exceed the risk limit.
For this reason, we have to choose the round sizes of a Minerva 
audit a priori.
For this paper, we consider two choices of round sizes.
For both, we estimate and then use the minimum first round size 
which achieves
a $90\%$ probability of stopping.
Then, for subsequent rounds, we either (i) multiply the previous
round size by a factor of $1.5$ and samples this many new ballots 
or (ii) multiply by a factor of $1$ and sample this many.
We choose $1.5$ because it gives a very rough approximation of the
round sizes which give a $90\%$ probability of stopping.
We choose $1$ because it may reflect a practical way to continue an
audit; if election officials have selected some first round size within
reasonable logistical bounds, drawing the same sample in subsequent rounds
could be practical.

\subsubsection{Roundsizes with Multiple of $1.5$}

\includegraphics[scale=.7]{minerva_multiround_1p5x_10^6/total_risk.png}

\subsubsection{Roundsizes with Multiple of $1.0$}

@@

>>>>

\subsection{Minerva}
For Minerva, it has not been shown that round sizes can be chosen
during the audit. That is, an adversary with knowledge of the history
of the audit may be able to choose round sizes which cause the 
risk of the audit to exceed the risk limit.
For this reason, we have to choose the round sizes of a Minerva 
audit a priori.
For this paper, we consider two choices of round sizes.
For both, we estimate and then use the minimum first round size 
which achieves
a $90\%$ probability of stopping.
Then, for subsequent rounds, we either (i) 
draw the same number of ballots in each round or (ii)
multiply the previous round size by a factor of $1.5$ and 
sample this many new ballots.
We consider the case of drawing samples of the same size
because it may reflect a practical way to continue an
audit; if election officials have selected some first round size within
reasonable logistical bounds, drawing the same number of 
ballots in subsequent rounds may be practical.
We also consider round sizes with samples increasing by a multiple
of $1.5$ because this multiple gives a very rough approximation of 
round sizes with a $90\%$ probability of stopping.

\subsubsection{Round Sizes with Multiple of $1.0$}

As with the preceding simulations, we ran $10,000=10^4$ trials
per state for both the underlying tie and underlying announced
outcome.

@@

[Fig above] shows that all simulations had a risk of less than 
$.1$, the risk limit. 
Unlike EOR BRAVO, the risks here are much closer to the risk limit,
showing that Minerva stops on average with sharper risk.

\subsubsection{Round Sizes with Multiple of $1.5$}

%For the Minerva simulations with a round size multiple of $1.5$,
%we increased the number of simulations to $10^6$ per state for 
%both an underlying tie and underlying announced outcome.

%\includegraphics[scale=.7]{minerva_multiround_1p5x_10^6/total_risk.png}
